data_cleaning_longer_period

### 2023-08-15 code/analysis_Redo.Rmd
lots of splits, need to standardize next

@@

summary(as.numeric(dfc[dfc$Year == 2010,]$months_of_cash))
summary(dfc[dfc$Year == 2010,]$ngla_net_gain_loss / dfc[dfc$Year == 2010,]$ngla_revenue)

did2s(
      data = dfc %>% 
        select(ID, Year, Tx, STATE, Sites, htn.rate, dm.rate, imm.rate, crc.rate, pap.rate, childbmi.rate, adultbmi.rate, ivd.rate, cad.rate, asthma.rate, Total, ngla_net_gain_loss, ngla_revenue, ngla_expense, Staff, months_of_cash, quick_ratio, fringe_rate) %>% 
        mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6, 
               CostPerPat = ngla_expense / Total, 
               months_of_cash = as.numeric(months_of_cash),
               quick_ratio = as.numeric(quick_ratio),
               fringe_rate = as.numeric(fringe_rate)) %>% 
        inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.03) 
                   %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
      yname = "Qcomp", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

event_study(data = dfc %>% mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate) / 6) %>% 
              inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.03)#as.numeric(months_of_cash) < 2)#Total > 10000) 
                   %>% select(ID) %>% unique() , by = c("ID")), 
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)

>>>>

## Overall average effects

## Effects stratified by profitability

## Effects startified by clinic size

## Changes in geographic distribution of resources by Distance to competitive zip

## Rival selecting where to put new site

Splits
- Total at 10000 and at 25000
- ngla_net_gain_loss/ngla_revenue at 0.03 (Profitable grow and give up financial footing, unprofitable improve quality)
- Months of cash at 2

Significant Variables
- Qcomp
- Total
- Sites
- Staff
- Quick-ratio

@@

summary(as.numeric(dfc[dfc$Year == 2010,]$Total))
summary(as.numeric(dfc[dfc$Year == 2010,]$months_of_cash))
summary(dfc[dfc$Year == 2010,]$ngla_net_gain_loss / dfc[dfc$Year == 2010,]$ngla_revenue)

did2s(
      data = dfc %>% 
        select(ID, Year, Tx, STATE, Sites, htn.rate, dm.rate, imm.rate, crc.rate, pap.rate, childbmi.rate, adultbmi.rate, ivd.rate, cad.rate, asthma.rate, Total, ngla_net_gain_loss, ngla_revenue, ngla_expense, Staff, months_of_cash, quick_ratio, fringe_rate, Assets, Liabilities) %>% 
        mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6, 
               CostPerPat = ngla_expense / Total, 
               months_of_cash = as.numeric(months_of_cash),
               Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / Assets, 
               Efficiency = ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities, 
               Altman = 6.56 * Liquidity + 3.26 * Profitability + 6.72 * Efficiency + 1.05 * NetWorth) %>% 
        inner_join(dfc %>% filter(Year == 2010 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
                   %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
      yname = "Qcomp", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

event_study(data = dfc %>% mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate) / 6) %>% 
              inner_join(dfc %>% filter(Year == 2010 & Total > 10000)# ngla_net_gain_loss/ngla_revenue < 0.03 as.numeric(months_of_cash) < 2)#Total > 10000) 
                   %>% select(ID) %>% unique() , by = c("ID")), 
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None) %>% 
  filter(abs(term) <= 5) %>% 
  #filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)

### 2023-08-15 code/data_cleaning_longer.Rmd
updated code
lots of splits, need to standardize next

staffing <- read.csv("/Users/jhm65/Dropbox/Git/Data/FQHC_Staffing.csv")

fins.revenue.expenses <- uds.cw %>% filter(Year == 2011) %>% unique() %>% select(ModernGranteeID, BHCMIS.ID) %>% 
  left_join(cw, by = c("ModernGranteeID" = "Grant Number")) %>% 
  left_join(fins.revenue.expenses, by = c("EIN" = "EIN")) %>% 
  select(ModernGranteeID:EIN, form_year:fringe_rate) %>% 
  left_join(staffing %>% select(EIN:Staff), by = c("EIN","form_year" = "Year"))
```

@@

df.comp <- df.comp %>% 
  group_by(ID) %>% 
  mutate(Class.random = ifelse(Class == "0 - Control", sample(class.vec, size = 1, replace = T), Class), 
         att.random = ifelse(Class == "0 - Control", sample(included.treat, size = 1, replace = T), att)) %>% 
                                 mutate(Tx = ifelse(Year >= att & att > 0, 1, 0)) %>% 
  filter(Year %in% included.years) %>% 
  mutate(year.rel = as.factor(ifelse(att.random > 0, Year - att.random, NA)), 
         Treatment = ifelse(att > 0, 1, 0)) %>% 
  select(BHCMISID:STATE, Name:ID, ACA:Treatment, Total:dm.total, fs_contributions:Staff)

>>>>

staffing <- read.csv("/Users/jhm65/Dropbox/Git/Data/FQHC_Staffing.csv")
assliabs <- read.csv("/Users/jhm65/Dropbox/Git/Data/FQHC_Assets_and_Liabilities.csv")

fins.revenue.expenses <- uds.cw %>% filter(Year == 2011) %>% unique() %>% select(ModernGranteeID, BHCMIS.ID) %>% 
  left_join(cw, by = c("ModernGranteeID" = "Grant Number")) %>% 
  left_join(fins.revenue.expenses, by = c("EIN" = "EIN")) %>% 
  select(ModernGranteeID:EIN, form_year:fringe_rate) %>% 
  left_join(staffing %>% select(EIN:Staff), by = c("EIN","form_year" = "Year"))

## Fixing some dumb mistake

# fixing.cw <- cbind(NewEINs = EINs[c(1:21, 23:323, 325:499, 501:617, 619:669, 671:738,  740:782, 784:790, 792:819, 821:989, 991:1106, 1108:1184, 1186)], 
#       assliabs %>% 
#   mutate(ch = Year - lag(Year)) %>% 
#   filter(is.na(ch) | ch < 0)) %>% 
#   mutate(Y = lead(X) - 1) %>% 
#   select(EIN, NewEINs, X, Y)
# 
# 
# for (k in 1:max(assliabs$X)){
#   assliabs[k,]$EIN <- assliabs[k,] %>% 
#     left_join(fixing.cw, by = c("EIN")) %>% 
#     filter(X.x >= X.y & X.x <= Y) %>% 
#     select(NewEINs) %>% 
#     unlist()
# }

fins.revenue.expenses <- fins.revenue.expenses %>% 
  left_join(assliabs %>% select(EIN:Liabilities), by = c("EIN","form_year" = "Year"))

@@

df.comp <- df.comp %>% 
  group_by(ID) %>% 
  mutate(Class.random = ifelse(Class == "0 - Control", sample(class.vec, size = 1, replace = T), Class), 
         att.random = ifelse(Class == "0 - Control", sample(included.treat, size = 1, replace = T), att)) %>% 
                                 mutate(Tx = ifelse(Year >= att & att > 0, 1, 0)) %>% 
  filter(Year %in% included.years) %>% 
  mutate(year.rel = as.factor(ifelse(att.random > 0, Year - att.random, NA)), 
         Treatment = ifelse(att > 0, 1, 0)) %>% 
  select(BHCMISID:STATE, Name:ID, ACA:Treatment, Total:dm.total, fs_contributions:Liabilities)
